Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-09 paper.tex
False starts on 'direct interaction' section.

\subsection{Growable}
The Nell system aims to have a ``low floor and no ceiling.''  The low
floor is a very simple base system, usable with no literacy skills or
external guidance.  The system then grows with the child's expanding
capabilities, serially accumulating story modules to tackle topics of
increasing difficulty.  As mentioned before, the ability for third
parties to independently author story modules is necessary to ensure
Nell can continue to grow.  There should be no external dependencies
limiting a child's ability to participate in this process: a Nell
system should contain a story editor and everything necessary to
author and publish story modules.

@@

\subsection{Direct interaction}
% constructionist?
% handwriting as UI?
% motor skills
% photo of XO-3?
The Nell system is tied to its implementation on a tablet computer.
It's no accident that the Nell system is instantiated on a tablet.
XXX

>>>>

\subsection{Growable}
The Nell system aims to have a ``low floor and no ceiling.''  The low
floor is a very simple base system, usable with no literacy skills or
external guidance.  The system then grows with the child's expanding
capabilities, serially accumulating story modules to tackle topics of
increasing difficulty.  As mentioned before, the ability for third
parties to independently author story modules is necessary to ensure
Nell can continue to grow.  There should be no external dependencies
limiting a child's ability to participate in this process: a Nell
system contains a story editor and everything necessary to
author and publish story modules.

@@

\subsection{Direct interaction}
% constructionist?
% handwriting as UI?
% motor skills
% photo of XO-3?

The Nell system is tied to its implementation on a tablet computer.

It's no accident that the Nell system is instantiated on a tablet.

The constructionist learning philosophy seeks to engage kids by
``making things''.  We believe that the direct interaction afforded by
tablet computing helps approach that goal.

Nell is deployed on a tablet computer, and...

Nell's implementation on a tablet computer advances...

\textbf{XXX}
